Study on the degree of transparency of the local public administration in Romania

### 2022-06-14 Article.Rmd
14.06.2022

---
title             : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
shorttitle        : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
author: 
  - name          : "Mari-Isabella Stan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1"
    email         : "stanisabella@yahoo.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Tănase Tasențe"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania, Faculty of Law and Administrative Sciences"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib", "transparenta.bib"]
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
documentclass     : "apa7"
classoption       : "man"
output            :
  word_document   : papaja::apa6_docx
  pdf_document    : papaja::apa6_pdf
header-includes:
  - \usepackage{ragged2e}
---

>>>>

---
title: Study on the degree of transparency of the local public administration in Romania
  in a pandemic context
author:
- name: Mari-Isabella Stan
  affiliation: '1'
  corresponding: yes
  address: '1'
  email: stanisabella@yahoo.com
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Cristian Opariuc-Dan
  affiliation: '1'
  role:
  - Writing - Review & Editing
  - Supervision
- name: Tănase Tasențe
  affiliation: '1'
  role:
  - Writing - Review & Editing
  - Supervision
shorttitle: Study on the degree of transparency of the local public administration
  in Romania in a pandemic context
output:
  html_document:
    df_print: paged
  pdf_document: papaja::apa6_pdf
  word_document: papaja::apa6_docx
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  <!-- https://tinyurl.com/ybremelq -->
keywords: keywords
wordcount: X
bibliography:
- r-references.bib
- transparenta.bib
floatsintext: no
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: man
affiliation:
- id: '1'
  institution: Ovidius University of Constanța, Romania, Faculty of Law and Administrative
    Sciences
header-includes: \usepackage{ragged2e}
---
